---
title: "Sal Reading 16S rRNA amplicons"
author: "Julian Trachsel"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Outline  
  
1. Mock Reading vs Mock Mock  
2. Mreading vs BBS866
3. Mreading vs AVIPRO  

## Mock Reading vs Mock Mock {.tabset}  
  
> E. Reading Challenge effect on turkey microbiome
Samples: Mock-vaccinated/mock-challenged and mock-vaccinated/Reading-challenged @ 2,7, 14, 21 dpi
Question: did challenge with Salmonella Reading alter the microbial composition of the turkey cecum (cecal contents)  
  
  
  
### Summary  
  
It is difficult to generate a robust answer to this question with the current data.    
  
Hard to say what the 'challenge' effect is with this subset.  Before challenge both groups are already quite different from each other.  Furthermore, over the course of the challenge both groups change quite a bit, not just the Reading infected group.  
  
- mock mock changes a lot
- mock Reading changes a lot
- Both rooms start out quite different from each other.  
  


  
### Questions  


Comparison #1 @ 2dpi:  
12 Mock-vaccinated/mock-challenged turkeys:        MM_D2 #1-12
VERSUS
12 mock-vaccinated/Reading-challenged turkeys:    Mreading_D2 #1-12

Comparison #2 @ 7dpi:
12 Mock-vaccinated/mock-challenged turkeys:        MM_D7 #1-12
VERSUS
12 mock-vaccinated/Reading-challenged turkeys:    Mreading_D7 #1-12

Comparison #3 @ 14dpi:
12 Mock-vaccinated/mock-challenged turkeys:        MM_D14 #1-12
VERSUS
12 mock-vaccinated/Reading-challenged turkeys:    Mreading_D14 #1-12

Comparison #4 @ 21dpi:
16 Mock-vaccinated/mock-challenged turkeys:        MM_D21 #1-16
VERSUS
16 mock-vaccinated/Reading-challenged turkeys:    Mreading_D21 #1-16

### Results  

```{r}


```



## Mreading vs BBS866 {.tabset}  
  
>  F. BBS 866 vaccination effect on Reading-challenged turkey microbiome
# Samples: Mock-vaccinated/Reading-challenged and BBS866-vaccinated/Reading-challenged
# Question: Did BBS 866 vaccination modify the Reading-induced alterations of the microbial composition of the turkey cecum (cecal contents)
  
  
  
### Summary  
  

  


  
### Questions  


Comparison #1 @ 2dpi:
12 mock-vaccinated/Reading-challenged turkeys:    Mreading_D2 #1-12
VERSUS
12 BBS866-vaccinated/Reading-challenged turkeys:    BBS866_OO_D2 #1-12

Comparison #2 @ 7dpi:
12 mock-vaccinated/Reading-challenged turkeys:    Mreading_D7 #1-12
VERSUS
12 BBS866-vaccinated/Reading-challenged turkeys:    BBS866_OO_D7 #1-12

Comparison #3 @ 14dpi:
12 mock-vaccinated/Reading-challenged turkeys:    Mreading_D14 #1-12
VERSUS
12 BBS866-vaccinated/Reading-challenged turkeys:    BBS866_OO_D14 #1-12

Comparison #4 @ 21dpi:
16 mock-vaccinated/Reading-challenged turkeys:    Mreading_D21 #1-16
VERSUS
16 BBS866-vaccinated/Reading-challenged turkeys:    BBS866_OO_D21 #1-16

### Results  

```{r}


```


## Mreading vs AVIPRO {.tabset}  
  
>  G. AviPro vaccination effect on Reading-challenged turkey microbiome
Samples: Mock-vaccinated/Reading-challenged and AviPro-vaccinated/Reading-challenged
Question: Did AviPro vaccination modify the Reading-induced alterations of the microbial composition of the turkey cecum (cecal contents)

  
  
  
### Summary  
  

  


  
### Questions  


Comparison #1 @ 2dpi:
12 mock-vaccinated/Reading-challenged turkeys:    Mreading_D2 #1-12
VERSUS
12 AviPro -vaccinated/Reading-challenged turkeys:    Avipro_OO_D2 #1-12

Comparison #2 @ 7dpi:
12 mock-vaccinated/Reading-challenged turkeys:    Mreading_D7 #1-12
VERSUS
12 AviPro -vaccinated/Reading-challenged turkeys:    Avipro_OO_D7 #1-12

Comparison #3 @ 14dpi:
12 mock-vaccinated/Reading-challenged turkeys:    Mreading_D14 #1-12
VERSUS
12 AviPro -vaccinated/Reading-challenged turkeys:    Avipro_OO_D14 #1-12

Comparison #4 @ 21dpi:
16 mock-vaccinated/Reading-challenged turkeys:    Mreading_D21 #1-16
VERSUS
13 AviPro -vaccinated/Reading-challenged turkeys:    Avipro_OO_D21 #1-13



### Results  

```{r}


```





### OTHER
***I don’t plan to necessarily compare the vaccines to one another, but instead create 2 manuscripts (if all the data allow). Although, it might be interesting to know, if both vaccines alter the microbiota, do they do it similarly; i.e.:
  1. Compare in A: comparison #1 & #2
2. Compare F to G on the corresponding dpi

  
