---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# manoj_16S

<!-- badges: start -->
<!-- badges: end -->

## TODO  

1) General ASV evaluation  
  - Contaminant ID, mock and NTC evaluation  
  - Index jumping?
    - Larsson AJ, Stanley G, Sinha R, Weissman IL, Sandberg R. Computational correction of index switching in multiplexed sequencing libraries. Nat Methods. 2018;15:305.  
  - reagent/lab contaminants?  
    - Decontam 
    - https://benjjneb.github.io/decontam/vignettes/decontam_intro.html 


The goal of manoj_16S is to ...

Title and description of the project. Something Vaccine, Salmonella, Turkeys.  



Silva v138.1 training set for taxonomy classification:
https://zenodo.org/record/4587955/files/silva_nr99_v138.1_train_set.fa.gz?download=1

Species level:
https://zenodo.org/record/4587955/files/silva_nr99_v138.1_wSpecies_train_set.fa.gz?download=1

```{r cars}
summary(cars)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub.
